\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\customItem}[2]{
  \small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\item{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\itemListStart}{\begin{itemize}}
\newcommand{\itemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/JustinButler700}{\Large Justin Butler}} & Email : \href{mailto:justinbutler700@gmail.com}{justinbutler700@gmail.com}\\
  \href{https://github.com/JustinButler700}{https://github.com/JustinButler700} & Mobile : {Hidden on Github} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Amazon}{Irvine, CA}
      {Software Engineer}{August 2023 - Present}
      \itemListStart
      \item{Optimized Echo device memory utilization by transitioning IPC libraries.}
      \item{Resolved Echo device display rendering bugs in C++ by analyzing logs and intuitively fixing misbehaving functions, enhancing user interface experience.}
      \item{Built integration testing bots using Python to ensure code convention and quality standards.}
      \itemListEnd


    \resumeSubheading
      {Wicis Health}{San Marcos, CA}
      {Freelance Software Engineer}{March 2023 - October 2023}
      \itemListStart
        \item
          {Created and maintained relational databases, with AWS RDS, and webhooks with AWS Lambda to ensure scalable management of data.}
        \item
          {Engineered a live email notification system to monitor vital data from telehealth devices, employing AWS SES for swift alerts to patients' physicians upon detection of abnormal readings.}
      \itemListEnd


    \resumeSubheading
      {Amazon}{Irvine, CA}
      {Software Engineer Intern}{May 2022 - Aug 2022}
      \itemListStart
        \item
          {Achieved a 100x reduction in Bluetooth latency on Alexa Gadgets by creating an Android backend service using Java, reducing latency from 600ms to a TP90 of less than 5ms.}
        \item
          {Developed latency profiling Alexa skills using Node.js and APL which ensured accurate RTT calculations.}
      \itemListEnd

    \resumeSubheading
      {Freelance}{Murrieta, CA}
      {Data Structures \& Assembly Language Tutor}{September 2020 - September 2021}
      \itemListStart
        \item
          {Guided students in mastering data structures and algorithms by providing personalized coaching, resulting in a more comprehensive understanding of the material.}
      \itemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/CS-441-Group-8/registore-electron}{\textbf{Point of Sales System : }}}
      {Developed a point-of-sale system using Typescript, GraphQL, and Electron.js. The system seamlessly integrates inventory management, accounts payable, and checkout into a user-friendly application.}
    \resumeSubItem{\href{https://twitter.com/MemeAutomaton}{\textbf{Twitter Meme Bot : }}}
      {Developed and launched a Twitter meme bot using Java, Twitter4J, and the Twitter developer API. The bot was created as a fun personal project.}
    \resumeSubItem{\textbf{Alexa APL Extension : }}
      {Created the "Gadgets extension" for Amazon Echo devices that utilizes async Protobuf packet transmission and reception to reduce Bluetooth latency significantly.}
    \resumeSubItem{\href{http://3.101.224.164:3000/}{\textbf{Zillow Clone : }}}
      {Built a React based, proof of concept Zillow clone project to be presented to JP Morgan Chase. (Hosted on an AWS EC2 )}
  
  \resumeSubHeadingListEnd

  %--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C++, Java, Python, Javascript, C, C\#, SQL, GraphQL, BASH, PHP, Kotlin, x86, ARM, Ruby, Typescript}
      \hfill
    }
    \item{
    \textbf{Technologies / Frameworks}{: AWS, GCP, Django, Docker, React, Gradle, Angular, Electron, Jira, Maven, Linux, Git, MongoDB, GoogleTest}
    }
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California State University San Marcos}{San Marcos, CA}
      {Bachelors of Science in Computer Science;  GPA: 3.80}{Aug. 2018 -- Dec. 2022}
  \resumeSubHeadingListEnd

  \begin{comment}
  \section{Coursework}
  \resumeSubHeadingListStart
    \item{
      \textbf{Courses}{: Cloud Computing, Embedded Systems, Web Development, Operating Systems \& Architecture, Database Systems, Software Engineering, Data Structures \& Algorithms}
      \hfill
    }
  \resumeSubHeadingListEnd
  \end{comment}



%-------------------------------------------
\end{document}
